---
title: "Bellabeat: Google Data Analytics Capstone"
author: "Kati Kimble"
date: "2023-06-24"
output: html_document
---

### R Markdown


#### **Table of Contents**

- [1. Summary](#section-1)
- [2. Ask](#section-2)
  - [2.1 Stakeholders](#section-2.1)
  - [2.2 Products](#section-2.2)
  - [2.3 Questions](#section-2.3)
  - [2.4 Business Task](#section-2.4)
  - [2.5 Limitations](#section-2.5)
- [3. Prepare](#section-3)
  - [3.1 Data Source Information](#section-3.1)
  - [3.2 Accessibility and Privacy](#section-3.2)
  - [3.3 Selected Datasets](#section-3.3)
- [4. Process](#section-4)
  - [4.1 Packages and Libraries](#section-4.1)
  - [4.2 Importing Datasets](#section-4.2)
  - [4.3 Preview Datasets](#section-4.3)
  - [4.4 Cleaning Datasets](#section-4.4)
  - [4.5 Merging Datasets](#section-4.5)
- [5. Analyze & Share](#section-5)
  - [5.1 Statistical Summary](#section-5.1)
  - [5.2 Heatmap: Data Entry Percentage](#section-5.2)
  - [5.3 Pie Chart: Time Asleep vs Time In Bed](#section-5.3)
  - [5.4 Pie Chart: User Sleep Type](#section-5.4)
  - [5.5 Bar Chart: Sleep on Weekdays vs Weekends](#section-5.5)
  - [5.6 Bar Charts: Average Calories Burned & Steps Taken Per Day](#section-5.6)
  - [5.7 Scatter Plot: Steps Taken & Calories Burned](#section-5.7)
  - [5.8 Scatter Plot: Correlation of Sleep & Activity Levels](#section-5.8)
- [6. Act](#section-6)
  - [6.1 Sleep and Sleep Quality](#section-6.1)
  - [6.2 Differentiating Weekday and Weekend Behavior](#section-6.2)
  - [6.3 Correlation Between Steps Taken and Calories Burned](#section-6.3)
  - [6.4 Sedentary Behavior and Sleep](#section-6.4)
  - [6.5 User Engagement](#section-6.5)
  - [6.6 Enhancing Weight and BMI Tracking](#section-6.6)


#### **1. Summary** {#section-1}

Bellabeat is a leading technology company that specializes in creating innovative smart products with a focus on health and wellness. Their range of smart devices collects valuable data on various aspects of health, including activity levels, sleep patterns, stress levels, and reproductive health. By providing women with access to this data, Bellabeat empowers them to gain insights into their own health and daily habits.

#### **2. Ask** {#section-2}

##### &emsp;2.1 *Stakeholders* {#section-2.1}

- **Urška Sršen:** Bellabeat’s cofounder and Chief Creative Officer
- **Sando Mur:** Mathematician and Bellabeat’s cofounder; key member of the Bellabeat executive team
- **Bellabeat marketing analytics team**

##### &emsp;2.2 *Products* {#section-2.2}
- **Bellabeat app:** Provides health data to users
- **Leaf:** An accessory that tracks activity, sleep, and stress
- **Time:** A wellness watch that tracks activity, sleep, and stress
- **Spring:** A smart water bottle that ensures proper hydration

##### &emsp;2.3 *Questions* {#section-2.3}
- What are some trends in smart device usage?
- How could these trends apply to Bellabeat customers?
- How could these trends help influence Bellabeat marketing strategy?

##### &emsp;2.4 *Business Task* {#section-2.4}
In this case study, our primary goal is to analyze the fitness data obtained from Bellabeat's smart devices and uncover potential growth opportunities for the company. Our focus will be on identifying valuable trends that can aid in making informed business decisions to drive the company's success.

##### &emsp;2.5 *Limitations* {#section-2.5}
The data analysis has limitations, including the fact that it represents only one month of data, making it potentially less comprehensive for capturing long-term trends. The data is also dated for 2016, not reflecting current business or market conditions. Additionally, there are missing values within the dataset, which can introduce bias and affect the accuracy of the analysis.  Only 30 eligible Fitbit users consented to the submission of the tracker data.  It's important to consider these limitations when interpreting the results.

#### **3. Prepare** {#section-3}
The data used in this analysis was provided by Bellabeat's cofounder and Chief Creative Officer,  Urška Sršen.  It can be found on Kaggle.com, titled [FitBit Fitness Tracker Data](https://www.kaggle.com/datasets/arashnic/fitbit).

##### &emsp;3.1 *Data Source Information* {#section-3.1}
This dataset generated by respondents to a distributed survey via Amazon Mechanical Turk between 03.12.2016-05.12.2016. Thirty eligible Fitbit users consented to the submission of personal tracker data, including minute-level output for physical activity, heart rate, and sleep monitoring.  There are 18 different csv files, with some of them being merged datasets. 

##### &emsp;3.2 *Accessibility and Privacy* {#section-3.2}
This data is open source with no copyright. It was last updated 3 years ago. The dataset usability score, on Kaggle, is 10.00.

##### &emsp;3.3 *Selected Datasets* {#section-3.3}
We will study three datasets for this analysis including:

- dailyActivity_merged.csv
- sleepDay_merged.csv
- weightLogInfo_merged.csv

These three datasets provide valuable user information including activity levels, sleep records, calorie and weight readings.

#### **4. Process** {#section-4}
We will use R for this analysis due to the statistical capabilities, the variety of packages available, and the strong visualization tools.  Furthermore, R Markdown allows for clean and easy to follow documentation and presentation, which makes it easier for stakeholders to understand the project and results.

##### &emsp;4.1 *Packages and Libraries* {#section-4.1}

```{r, message=FALSE, warning=FALSE, error=FALSE}
install.packages("tidyverse")
install.packages("here")
install.packages("skimr")
install.packages("janitor")
install.packages("lubridate")
install.packages("ggrepel")
      

library(tidyverse)
library(here)
library(skimr)
library(janitor)
library(lubridate)
library(ggrepel)
library(gridExtra)
```

##### &emsp;4.2 *Importing Datasets* {#section-4.2}

```{r, message=FALSE, warning=FALSE, error=FALSE}
daily_activity <- read_csv(file = "../input/fitbit/Fitabase Data 4.12.16-5.12.16/dailyActivity_merged.csv")
sleep_day <- read_csv(file="../input/fitbit/Fitabase Data 4.12.16-5.12.16/sleepDay_merged.csv")
weight_log <- read_csv(file="../input/fitbit/Fitabase Data 4.12.16-5.12.16/weightLogInfo_merged.csv")
```

##### &emsp;4.3 *Preview Datasets* {#section-4.3}
We use head() and str() functions to get a quick summary of our data.  Here we can explore column names, datatypes, and range.

```{r}
head(daily_activity)
str(daily_activity)

head(sleep_day)
str(sleep_day)

head(weight_log)
str(weight_log)
```

##### &emsp;4.4 *Cleaning Datasets* {#section-4.4}
We will check the number of unique users and duplicate rows in each data set.  We can do that with this code:

```{r}
n_unique(daily_activity$Id)
n_unique(sleep_day$Id)
n_unique(weight_log$Id)

sum(duplicated(daily_activity))
sum(duplicated(sleep_day))
sum(duplicated(weight_log))
```

We can use pipes in each dataset, to keep only unique rows, drop rows with missing values, rename the date column, and convert the date column to Date format.  

```{r}
daily_activity <- daily_activity %>%
  distinct() %>%
  drop_na() %>%
  rename(Date = ActivityDate) %>%
  mutate(Date = as.Date(Date, format = "%m/%d/%Y"))

sleep_day <- sleep_day %>% 
  distinct() %>%
  drop_na() %>%
  rename(Date = SleepDay) %>%
  mutate(Date = as.Date(Date, format = "%m/%d/%Y"))

weight_log <- weight_log %>%
  distinct() %>%
  mutate(Date = as.Date(Date, format = "%m/%d/%Y %I:%M:%S %p"))
```

There are no more duplicated rows in our datasets.

```{r}
sum(duplicated(daily_activity))
sum(duplicated(sleep_day))
sum(duplicated(weight_log))
```

##### &emsp;4.5 *Merging Datasets* {#section-4.5}
The datasets have been cleaned, now we will merge them together.

```{r}
merged_df <- merge(merge(daily_activity, sleep_day, by = c('Id', 'Date'), all = TRUE), weight_log, by = c('Id', 'Date'), all = TRUE)
```


```{r}
str(merged_df)
```

#### **5. Analyze & Share** {#section-5}
We will now perform an in-depth analysis on the processed data and communicate our findings to the stakeholders.

##### &emsp;5.1 *Statistical Summary* {#section-5.1}

```{r}
summary(merged_df)
```

In our dataset, we observe that the date range spans from April 12, 2016, to May 12, 2016. Additionally, we notice a considerable number of missing values (NA) in the WeightPounds column. To gain further insights, we will calculate the percentage of NA entries in comparison to the total number of entries.

```{r}
total_weight_entries <- nrow(merged_df)
na_count <- sum(is.na(merged_df$WeightPounds))

percentage_entries <- (total_weight_entries-na_count) / total_weight_entries *100
percentage_na <- na_count / total_weight_entries * 100
# Output the percentage of NA entries
percentage_na
```

##### &emsp;5.2 *Heatmap: Data Entry Percentage* {#section-5.2}
To gain insights into the completeness of the data analysis, I aimed to visualize the percentage of non-NA entries for each column in the dataset. This would help identify which columns contain a higher proportion of non-missing values and can contribute to a more comprehensive analysis.

I started by computing the percentage of non-NA entries in the dataset. This provided insights into the completeness of the data. Next, I created a heat map based on this information to visually represent the distribution of non-missing values across different columns.

```{r}
# Calculate the percentage of non-NA entries for each column
percentage_col_entries <- colMeans(!is.na(merged_df)) * 100

# Print the percentage of entries for each column
percentage_col_entries
```

```{r}
# Create a data frame for the heatmap
heatmap_data <- data.frame(
  column_names = names(percentage_col_entries),
  percentage = percentage_col_entries
)

# Sort the data frame by percentage in descending order
heatmap_data <- heatmap_data[order(heatmap_data$percentage, decreasing = TRUE), ]

# Create the heatmap using ggplot2 and geom_tile
ggplot(heatmap_data, aes(x = 1, y = reorder(column_names, -percentage))) +
  geom_tile(aes(fill = percentage), width = 1, height = 0.8) +
  scale_fill_gradient(low = "#F2F2F2", high = "#008080", name = "Percentage") +
  labs(x = "", y = "Column Names", title = "Percentage of Entries") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid = element_blank(),
  )
```

Upon reviewing the heat map and considering the distribution of non-missing values across columns, I made the decision to exclude the columns Fat, LogId, IsManualReport, and BMI from further analysis

##### &emsp;5.3 *Pie Chart: Time Asleep vs Time In Bed* {#section-5.3}
As I examined the dataset, I came across the columns "TotalMinutesAsleep" and "TotalTimeInBed," I became interested in delving deeper into this aspect to investigate the percentage of time users spend in bed engaged in activities other than sleeping compared to the time spent asleep. This analysis could provide valuable insights into users who may be experiencing insomnia or have disrupted sleep patterns.

```{r}
# add column to dataframe to calculate percentage users asleep to in bed
merged_df$percentage_asleep_inbed <- (merged_df$TotalMinutesAsleep / merged_df$TotalTimeInBed) * 100

# find average that are asleep in bed vs average in bed
average_asleep_inbed <- mean(na.omit(merged_df$percentage_asleep_inbed))
average_in_bed <- 100 - average_asleep_inbed

# make a pie chart for better visualization
values <- c(average_asleep_inbed, average_in_bed)
labels <- c("Asleep", "Awake")
colors <- c("#3366cc", "#ff9900")

df <-data.frame(group = labels, value = values)

pie <- ggplot(df, aes(x="", y=value, fill=group))+
  geom_bar(width = 1, stat = "identity") + 
  coord_polar("y", start = 0) + 
  theme_void() +
  geom_text(aes(label = paste0(round(value, 1), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = colors) + 
  labs(title = "Average Percentage of Time Spent Awake Versus Asleep in Bed")

pie
```

Based on the analysis, it appears that, on average, the majority of users tend to be asleep while in bed. The data suggests that a significant portion of the total time spent in bed is dedicated to sleep rather than engaging in other activities. 

##### &emsp;5.4 *Pie Chart: User Sleep Type* {#section-5.4}
According to the [CDC](https://www.cdc.gov/sleep/about_sleep/how_much_sleep.html), it is recommended that adults should aim for at least 7 hours of sleep per night. In our analysis, we will now focus on examining the dataset to categorize users based on their sleep duration.

To begin, we will create a new data frame that summarizes the average sleep time per user. This will provide a clear overview of the sleep patterns and help identify individuals who meet or fall short of the recommended sleep duration.

```{r}
daily_sleep_average <- merged_df %>%
  filter(complete.cases(TotalMinutesAsleep)) %>%
  group_by(Id) %>%
  summarise(mean_minutes_asleep = mean(TotalMinutesAsleep))

head(daily_sleep_average)
```

Following the creation of the average sleep time per user data frame, we will proceed to classify the users into three categories based on their sleep duration:

- Less than 7 hours = Inadequate Sleep
- 7 hours to 9 hours = Adequate Sleep
- Greater than 9 hours = Excess Sleep

Utilizing the "daily_sleep_average" dataset, we will leverage this information to calculate the percentage of users falling into each sleep type category. This analysis will provide insights into the distribution of sleep patterns among the users and help identify the prevalence of inadequate, adequate, and excess sleep durations within the dataset.

```{r}
user_sleep_type <- daily_sleep_average %>%
  mutate(user_sleep_type = case_when(
    mean_minutes_asleep < 420 ~ "Inadequate Sleep",
    mean_minutes_asleep >= 420 & mean_minutes_asleep <= 540 ~ "Adequate Sleep", 
    mean_minutes_asleep > 540 ~ "Excess Sleep"
  )) %>%
  
  # Mutate the data frame so we can see the percentages of each sleep type
  count(user_sleep_type) %>%
  mutate(percentage = prop.table(n) * 100)
```


```{r}
# Preview our new dataset
head(user_sleep_type)
```


```{r}
# Create the pie chart
pie_chart <- ggplot(user_sleep_type, aes(x = "", y = percentage, fill = user_sleep_type)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  theme_void() +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), position = position_stack(vjust = 0.5)) + labs(title = "Average of Users per Specified Sleep Type")

pie_chart
```

The visualization clearly illustrates that a significant portion of users in the dataset are not achieving an adequate amount of sleep according to the recommendations set forth by the CDC. This finding highlights the prevalence of insufficient sleep among the analyzed users.

##### &emsp;5.5 *Bar Chart: Sleep on Weekdays vs Weekends* {#section-5.5}

In order to examine the sleep patterns of users on weekdays versus weekends, we will add a new column to the "merged_df" dataset that specifies whether each date corresponds to a weekday or a weekend.

To achieve this, we will create a column named "day_type" in the "merged_df" dataset. This column will indicate whether each date falls on a weekday or a weekend. By categorizing the dates in this manner, we can then analyze and compare the sleep durations of users on weekdays and weekends to determine if there is a difference in their sleep habits during these periods.

We create a bar chart to visualize and compare the sleep durations of users on weekdays and weekends.

```{r}
merged_df <- merged_df %>%
  mutate(day_type = case_when(
    weekdays(Date) %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday") ~ "Weekday",
    weekdays(Date) %in% c("Saturday", "Sunday") ~ "Weekend"
  ))
```


```{r}
# Calculate the average sleep duration for weekdays and weekends
average_sleep_duration <- merged_df %>%
  group_by(day_type) %>%
  summarise(avg_sleep_duration = mean(TotalMinutesAsleep, na.rm = TRUE))
```


```{r}
# Create a Bar Chart
sleep_chart <- ggplot(average_sleep_duration, aes(x = day_type, y = avg_sleep_duration)) +
  geom_col(fill = c("Weekday" = "orange", "Weekend" = "purple")) +
  labs(x = "Day Type", y = "Average Sleep Duration (minutes)", title = "Average Sleep Duration on Weekdays vs. Weekends")

sleep_chart
```

Based on the bar chart analysis, it appears that there is a slight difference in sleep duration between weekdays and weekends. Most users tend to get slightly more sleep on the weekends compared to weekdays. Although the difference may be minimal, this finding suggests that users have the opportunity to catch up on sleep or follow a different sleep routine during weekends, resulting in slightly longer sleep durations.

##### &emsp;5.6 *Bar Charts: Average Calories Burned & Steps Taken Per Day* {#section-5.6}
Having added the "day_type" column to our "merged_df" dataset, we can now delve into exploring other data that may exhibit correlations with this information.

To begin, we will calculate the average calories burned and steps taken for each day. Subsequently, we will create separate bar charts to visually represent these averages.

```{r, message=FALSE, warning=FALSE, error=FALSE}
# Calculate average calories burned and steps taken for each week day and day type
averages_df <- merged_df %>%
  group_by(weekday = weekdays(Date), day_type) %>%
  summarise(avg_calories_burned = mean(Calories), avg_steps = mean(TotalSteps), na.rm = TRUE)

# Create a bar chart of average calories burned throughout the week
ggplot(averages_df, aes(x = weekday, y = avg_calories_burned, fill = day_type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Days", y = "Average Calories Burned", title = "Average Calories Burned Throughout the Week") +
  scale_fill_manual(values = c("lightblue", "purple"), labels = c("Weekday", "Weekend")) +
  theme_minimal()

# Create a bar chart of average steps taken throughout the week
ggplot(averages_df, aes(x = weekday, y = avg_steps, fill = day_type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Days", y = "Average Steps Taken", title = "Average Steps Taken Throughout the Week") +
  scale_fill_manual(values = c("lightblue", "purple"), labels = c("Weekday", "Weekend")) +
  theme_minimal()
```


Based on our bar charts, it is evident that the highest number of calories burned occurs on Saturday and Tuesday, while the lowest number is observed on Thursday. Similarly, Saturday and Tuesday also show the highest number of steps taken, whereas Sunday reflects the lowest step count.

##### &emsp;5.7 *Scatter Plot: Steps Taken & Calories Burned* {#section-5.7}

To examine the correlation between steps taken and calories burned, we can create a scatter plot. This visualization will help us understand the relationship between these two variables.

```{r, message=FALSE, warning=FALSE, error=FALSE}
# Omitting NA values
steps_and_calories_df <- na.omit(merged_df[c("TotalSteps", "Calories")])

# Formula for printing the coefficient and rounding
cor_coeff <- function(x, y) {
  corr <- cor(x, y)
  paste("Correlation coefficient:", round(corr, 2))
}

# Create a scatter plot to view the coorelation between steps taken and calories burned
ggplot(steps_and_calories_df, aes(x = TotalSteps, y = Calories)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(x = max(merged_df$TotalSteps), y = max(merged_df$Calories),
            label = cor_coeff(merged_df$TotalSteps, merged_df$Calories),
            hjust = 1, vjust = 1) +
  labs(x = "Total Steps", y = "Calories") +
  ggtitle("Total Steps vs. Calories")
```

The scatter plot reveals a positive correlation between the number of steps taken and the calories burned. As the number of steps increases, there is a tendency for the calories burned to also increase. This positive correlation suggests that engaging in more physical activity, as indicated by a higher step count, leads to a higher calorie expenditure.

##### &emsp;5.8 *Scatter Plot: Correlation of Sleep & Activity Levels* {#section-5.8}
To examine the correlation between sleep and activity levels, we can create a new data frame that includes relevant variables and omit any rows with missing values (NA).

```{r}
# Filtered data frame
filtered_data <- na.omit(merged_df[c("TotalMinutesAsleep", "VeryActiveMinutes", "FairlyActiveMinutes", "LightlyActiveMinutes", "SedentaryMinutes")])
```


```{r}
# Creating our scatterplots
plot1 <- ggplot(filtered_data, aes(x = TotalMinutesAsleep, y = VeryActiveMinutes)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(x = max(filtered_data$TotalMinutesAsleep), y = max(filtered_data$VeryActiveMinutes),
            label = cor_coeff(filtered_data$TotalMinutesAsleep, filtered_data$VeryActiveMinutes),
            hjust = 1, vjust = 1) +
  labs(x = "Total Minutes Asleep", y = "Very Active Minutes") +
  ggtitle("Minutes Asleep vs. Very Active ")

plot2 <- ggplot(filtered_data, aes(x = TotalMinutesAsleep, y = FairlyActiveMinutes)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(x = max(filtered_data$TotalMinutesAsleep), y = max(filtered_data$FairlyActiveMinutes),
            label = cor_coeff(filtered_data$TotalMinutesAsleep, filtered_data$FairlyActiveMinutes),
            hjust = 1, vjust = 1) +
  labs(x = "Total Minutes Asleep", y = "Fairly Active Minutes") +
  ggtitle("Minutes Asleep vs. Fairly Active")

plot3 <- ggplot(filtered_data, aes(x = TotalMinutesAsleep, y = LightlyActiveMinutes)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(x = max(filtered_data$TotalMinutesAsleep), y = max(filtered_data$LightlyActiveMinutes),
            label = cor_coeff(filtered_data$TotalMinutesAsleep, filtered_data$LightlyActiveMinutes),
            hjust = 1, vjust = 1) +
  labs(x = "Total Minutes Asleep", y = "Lightly Active Minutes") +
  ggtitle("Minutes Asleep vs. Lightly Active")

plot4 <- ggplot(filtered_data, aes(x = TotalMinutesAsleep, y = SedentaryMinutes)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(x = max(filtered_data$TotalMinutesAsleep), y = max(filtered_data$SedentaryMinutes),
            label = cor_coeff(filtered_data$TotalMinutesAsleep, filtered_data$SedentaryMinutes),
            hjust = 1, vjust = 1) +
  labs(x = "Total Minutes Asleep", y = "Sedentary Minutes") +
  ggtitle("Minutes Asleep vs. Sedentary")
```

To facilitate comparison, I have consolidated all the plots into a single display.

```{r, message=FALSE, warning=FALSE, error=FALSE}
# Arrange four plots in a 2-column layout
grid.arrange(plot1, plot2, plot3, plot4, ncol = 2)
```

The scatterplots we analyzed indicate that, overall, there is little to no correlation between most of the variables we examined. However, one notable exception is the negative correlation observed between the "TotalMinutesAsleep" and "SedentaryMinutes" variables.

The negative correlation between "TotalMinutesAsleep" and "SedentaryMinutes" suggests that as the duration of total minutes asleep increases, the amount of time spent in a sedentary state decreases. This finding implies that individuals who sleep for longer durations tend to engage in less sedentary behavior during their waking hours.

#### **6. Act** {#section-6}
Based on the important findings from the analysis of the fitness company's data, we can make the following suggestions to the stakeholders:

##### &emsp;6.1 *Sleep and Sleep Quality* {#section-6.1}

- Enhance the sleep tracking capabilities of the smartwatch and leaf tracker to provide users with comprehensive insights into their sleep patterns, including sleep stages, efficiency metrics, and personalized sleep improvement recommendations.
- Educate users about the importance of sufficient and quality sleep, offering resources, tips, and personalized guidance within the app to help users establish healthy sleep routines and overcome common sleep issues.

##### &emsp;6.2 *Differentiating Weekday and Weekend Behavior*{#section-6.2}

- Consider offering targeted interventions or challenges focused on encouraging users to maintain consistent sleep patterns and healthy behaviors, especially on weekdays when sleep duration may be lower.
- Provide users with weekday-specific activity challenges or incentives to engage in higher levels of physical activity and burn more calories during inactive days. In this analysis, Sunday was the most inactive day of the week.

##### &emsp;6.3 *Correlation Between Steps Taken and Calories Burned* {#section-6.3}

- Use the positive correlation between steps taken and calories burned to motivate users to increase their physical activity levels. Offer rewards, challenges, and personalized goals to encourage users to reach and exceed their daily step targets.

##### &emsp;6.4 *Sedentary Behavior and Sleep* {#section-6.4}

- Promote the importance of reducing sedentary behavior during waking hours. Incorporate reminders or alerts within the app or smartwatch to encourage users to avoid prolonged sitting or sedentary activities.
- Emphasize the benefits of maintaining an active lifestyle and avoiding prolonged sedentary behavior for overall sleep quality and health.

##### &emsp;6.5 *User Engagement* {#section-6.5}

- Incorporate gamification elements and challenges within the app to encourage user participation, competition, and long-term engagement. Reward users for achieving milestones, meeting targets, and maintaining healthy habits.

##### &emsp;6.6 *Enhancing Weight and BMI Tracking*{#section-6.6}

- Given the low percentage of weight, BMI, and fat entries observed in the dataset, it could be beneficial for the fitness company to consider marketing a smart scale and body fat monitor that enables seamless communication with the app for easier and more accurate weight and BMI logging. By offering a convenient and integrated solution, users would be more motivated to track their weight and BMI regularly, resulting in a larger volume of weight data for analysis and better insights into their overall health and progress.


These suggestions aim to leverage the insights gained from the data analysis to improve users' sleep, activity levels, and overall well-being. It is important for the stakeholders to consider the specific needs and preferences of their users, align the suggestions with their company's goals, and continuously monitor and evaluate the effectiveness of implemented strategies.